City traffic, IoT and Blockchain technologies

### 2020-10-25 thesis/report2.tex
Another small paragraph.

>>>>

    Data assurance and resilience are two themes within the big concept of Blockchain security. In \cite{TowardsdatAassuranceAndResilience} the authors are describing a mechanism for drones that achieves few objectives like trusted data origin (allows to know for sure which drone send a part of data), instant and permanent data integrity ()
